Commutative Character Sheaves

### 2015-11-10 followup.tex
Started working on the proof for Section 3, again.

The abelianization $G\ab\ceq G/G\der$ exists in schemes over $\Fq$, and the quotient $q : G \to G\ab$ is faithfully flat and a $G\der$-torsor in the fppf topology \cite{SGA3}*{Expos\'e {VI}$_A$, Thm. 3.2}.

@@

\iffalse
We summarize the setup in a diagram.
\[
\begin{tikzcd}
{} & G\times G \arrow{d}{c} &&&\\
1 \arrow{r} & G\der \arrow{r}{} & G \arrow{r}{q} & G\ab \arrow{r} & 1
\end{tikzcd}
\]
\fi

@@

\subsection{Change of action/perspective}

Suppose there is some $f : H\times G\to G\times G$ such that the following diagram commutes.
%%%%%%%% FIX!!!! %%%%%%%%%%
\[
\begin{tikzcd}
\ &  \arrow{dl}[swap]{a} H \times G \arrow{dr}{p} \arrow{dd}[swap]{f} & \\
G & & G \\
& \arrow{ul}{m} G \times G \arrow{ur}[swap]{p_2} & 
\end{tikzcd}
\]
Then $f(h,g) = (a(h,g) g^{-1}, g)$.
Define $f_1: H\times G \to G$ by $f_1(h,g)\ceq a(h,g) g^{-1}$; then $f(h,g) = (f_1(h,g),g)$ and $f_1(h_1 h_2,g) = f_1(h_1, h_2\cdot g) f_1(h_2,g)$.

We now combine the material of the last two sections, by specializing to the following case: $H$ is a closed subgroup of $G$ and $q : G \to G/H$ is the fppf quotient.

\[
\begin{tikzcd}
\CS(H) & \arrow{l}[swap]{i^*} \CS(G) &\arrow{l}[swap]{q^*} 
\CS(G/H) \arrow{dl}{\text{`comparison'}} \\
 & \CS_{H}(G) \arrow{u}{\text{forget}}  & 
\end{tikzcd}
\]

\begin{lemma}
$\CS(G/H)$ is equivalent to the category of triples $(\cs{L},\mu,\beta)$ where $(\cs{L},\mu)\in \CS(G)$ and $\beta : \cs{L}\vert_H \to (\EE)_H$ is an isomorphism in $\CS(H)$, with morphisms $\alpha : (\cs{L},\mu,\beta) \to (\cs{L}',\mu',\beta')$ defined by the condition
$\alpha : (\cs{L},\mu) \to (\cs{L}',\mu')$ is a morphism in $\CS(G)$ and $\beta = \beta' \circ \alpha\vert_{H}$.
\end{lemma}

In this case, the action $a$ is the restriction of $m$ to $H\times G$ and $f : H \times G\to G\times G$ is simply the inclusion and $f_1: H\times G \to G$ is projection to the first coordinate followed by inclusion $H \hookrightarrow G$, so $f_1^*\cs{L} = \cs{L}\vert_{H} \boxtimes (\EE)_G$. 
Then $\beta_1 : f_1^*\cs{L} \to (\EE)_{H\times G}$ determines an isomorphism $\beta : \cs{L}\vert_{H} \to (\EE)_{H}$, and vice versa.
Moreover, in this case, the constraint on $\beta$ is only this: $\beta : \cs{L}\vert_{H} \to (\EE)_{H}$ is an isomorphism in $\CS(H)$. 
%Let $\CS^H(G)$ denote the category of triples $(\cs{L},\mu,\beta)$ where $(\cs{L},\mu)\in \CS(G)$ and $\beta : \cs{L}\vert_H \to (\EE)_H$ is an isomorphism in $\CS(H)$.

@@

\begin{proof}[Proof of Proposition~\ref{prop:Gder_triv}]
We now consider a special case of the lemmas above. 
Suppose $H = G\der$ and the action $a$ is the restriction of $m$ to $G\der\times G$.
Then $f : G\der \times G\to G\times G$ is simply the inclusion and $f_1: G\der\times G \to G$ is projection to the first coordinate followed by inclusion $G\der \hookrightarrow G$.

As we have seen above, the fppf quotient $q : G\to G\ab = G/G\der$ exists in schemes.
Moreover, the quotient $q : G \to G\ab$ is faithfully flat and a $G\der$-torsor in the fppf topology, by\cite{SGA3}*{Expos\'e {VI}$_A$, Thm. 3.2}
%(In fact, it's a trivial torsor in that topology.)
It now follows from Lemma~[] that the comparison functor $\CS(G\ab)\to \CS_{G\der}(G)$ is an equivalence.
On the other hand, by Lemma~[], the forgetful functor $\CS_{G\der}(G)\to \CS(G)$ defines an equivalence $\CS_{G\der}(G)\to \CS'(G)$, where $\CS'(G)$ is the category of $(\cs{L},\mu,\beta)$ where $(\cs{L},\mu)\in \CS(G)$ and $\beta : \cs{L}\vert_{G\der} \iso (\EE)_{G\der}$ in $\CS(G\der)$.
\end{proof}

\begin{proof}[Proof of Proposition~\ref{prop:Gdiagram}]

@@

\begin{proof}[Proof of Theorem~\ref{thm:Gab}] 
\end{proof}

@@

>>>>

@@

@@

\subsection{Change of perspective}

We now suppose that $H$ is a subgroup of $G$ and that the action $a : H\times G\to G$ is obtained by restricting the action $m : G \times G\to G$ to $H\times G$.
Then we have the diagram
\[
\begin{tikzcd}
\ &  \arrow{dl}[swap]{a} H \times G \arrow{dr}{p} \arrow{dd}[swap]{f} & \\
G & & G \\
& \arrow{ul}{m} G \times G \arrow{ur}[swap]{p_2} & 
\end{tikzcd}
\]
where $f(h,g) = (a(h,g) g^{-1}, g) = (h,g)$.
%Define $f_1: H\times G \to G$ by $f_1(h,g)\ceq (i\circ p_1)$; then $f(h,g) = (f_1(h,g),g)$ and $f_1(h_1 h_2,g) = f_1(h_1, h_2\cdot g) f_1(h_2,g)$.
Then every $H$-equivariant linear character sheaf $(\cs{L},\mu, \nu)$ uniquely determines an isomorphism 
\[
\beta : \cs{L}\vert_H \to (\EE)_{H}
\]
by 
\[
\nu = (\beta \boxtimes \id_{\cs{L}}) \circ  f^*\mu,
\] 
or more precisely, by the following diagram of isomorphisms.
\[
\begin{tikzcd}
a^*\cs{L} \arrow{d}{m\circ f = a} \arrow{rrr}{\nu}
&&& p^*\cs{L}\\
f^* m^*\cs{L} \arrow{r}{f^*\mu} & 
f^*(\cs{L}\boxtimes \cs{L}) \arrow{r} & 
\cs{L}\vert_{H} \boxtimes \cs{L} \arrow{r}{\beta\boxtimes \id_{\cs{L}}} & 
(\EE)_{H} \boxtimes \cs{L} \arrow{u} 
\end{tikzcd}
\]
In this way we see we may replace $(\cs{L},\mu,\nu)$ with a triple, $(\cs{L},\mu,\beta)$, from which $(\cs{L},\mu,\nu)$ may be recovered.
The isomorphism $\beta : \cs{L}\vert_{H} \to (\EE)_{H}$ is constrained by two properties, corresponding to the diagrams in Sections [] and [].

\begin{lemma}
$\CS_H(G)$ is equivalent to the category of triples $(\cs{L},\mu,\beta)$ where $(\cs{L},\mu)\in \CS(G)$ and $\beta : \cs{L}\vert_H \to (\EE)_H$ is an isomorphism in $\CS(H)$, with morphisms $\alpha : (\cs{L},\mu,\beta) \to (\cs{L}',\mu',\beta')$ defined by the condition
$\alpha : (\cs{L},\mu) \to (\cs{L}',\mu')$ is a morphism in $\CS(G)$ and $\beta = \beta' \circ \alpha\vert_{H}$.
\end{lemma}

\begin{proof}
\end{proof}

@@

\begin{proof}[Proof of Proposition~\ref{prop:Gder_triv}]
The abelianization $G\ab\ceq G/G\der$ exists in schemes over $\Fq$
and the quotient $q : G \to G\ab$ is faithfully flat and a $G\der$-torsor in the fppf topology \cite{SGA3}*{Expos\'e {VI}$_A$, Thm. 3.2}.
Then
\[
\begin{tikzcd}
%{} & G\times G \arrow{d}{c} &&&\\
1 \arrow{r}{i} & G\der \arrow{r}{} & G \arrow{r}{q} & G\ab \arrow{r} & 1
\end{tikzcd}
\]
gives
\[
\begin{tikzcd}
\CS(H) & \arrow{l}[swap]{i^*} \CS(G) &\arrow{l}[swap]{q^*} 
\CS(G/H) \arrow{dl}{\text{`comparison'}} \\
\arrow{u}{\text{forget}} \CS'(G) \arrow{r}{\beta \mapsto \nu_\beta} & \CS_{H}(G) \arrow{u}{\text{forget}}  & 
\end{tikzcd}
\]
%
It now follows from Lemma~[] that the comparison functor $\CS(G\ab)\to \CS_{G\der}(G)$ is an equivalence.
On the other hand, by Lemma~[], $\CS_{G\der}(G)\to \CS'(G)$, defined by $(\cs{L},\mu,\nu)\mapsto (\cs{L},\mu, \beta_\nu)$, is an equivalence.
Since the essential image of the forgetful functor $\CS'(G)\to \CS(G)$ is precisely the category of $(\cs{L},\mu)\in \CS(G)$ such that $\cs{L}\vert_H \iso (\EE)_H$, this completes the proof of 
Proposition~\ref{prop:Gder_triv}.
\end{proof}

\begin{proof}[Proof of Theorem~\ref{thm:Gab}] 
\[
\begin{tikzcd}
\CS'(G) &\arrow{l}[swap]{q^*} 
\CS(G\ab) \arrow{l}{\text{`comparison'}} \\
\CCS(G) \arrow{u}{\text{forget}}  & \CCS(G\ab) \arrow{u} 
\end{tikzcd}
\]

@@

%\begin{proof}[Proof of Proposition~\ref{prop:Gdiagram}]
%\end{proof}

@@

Suppose there is some $f : H\times G\to G\times G$ such that the following diagram commutes.
\[
\begin{tikzcd}
\ &  \arrow{dl}[swap]{a} H \times G \arrow{dr}{p} \arrow{dd}[swap]{f} & \\
G & & G \\
& \arrow{ul}{m} G \times G \arrow{ur}[swap]{p_2} & 
\end{tikzcd}
\]
Then $f(h,g) = (a(h,g) g^{-1}, g)$.
Define $f_1: H\times G \to G$ by $f_1(h,g)\ceq a(h,g) g^{-1}$; then $f(h,g) = (f_1(h,g),g)$ and $f_1(h_1 h_2,g) = f_1(h_1, h_2\cdot g) f_1(h_2,g)$.

We now combine the material of the last two sections, by specializing to the following case: $H$ is a closed subgroup of $G$ and $q : G \to G/H$ is the fppf quotient, which exists in schemes by  . . .
